%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Shubham}{Sharma}{ \urlstyle{same} +91 8860315605 | \href{mailto:shubham9019@gmail.com}{shubham9019@gmail.com} | Gurgaon, Haryana
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Chandigarh University}
\descript{B.E Computer Science and Engineering}
\location{2017 - 2021 | Mohali, Punjab}
\sectionsep


\subsection{Delhi Public School, MK}
\location{2017 | Gurgaon, Haryana}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 

Github:// \href{https://github.com/shubham9019}{\bf shubham9019} \\
LinkedIn://  \href{https://www.linkedin.com/in/shubham9019}{\bf shubham9019} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}

.NET \textbullet{}   C\# \textbullet{} SQL Server \textbullet{} React  \textbullet{}\\ JavaScript \textbullet{} Entity Framework \textbullet{} Git \textbullet{} Azure
\textbullet{} Docker \textbullet{} CosmosDB \textbullet{} Kubernetes \textbullet{} Specflow \textbullet{}  WPF \textbullet{} \\WCF \textbullet{} Redis \textbullet{} AWS \textbullet{} Microservices \textbullet{} MongoDB \textbullet{} ActiveBatch
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Publicis Sapient}
\descript{| Associate Technology L1 }
\location{July 2022 - Present | Gurgaon, Haryana}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked on .NET Core Microservices along with WPF, WCF applications.
\item Improved the workflow of a major WPF application to save users from several hours of repetitive work.
\item Improved performance, identified and resolved bottlenecks and deadlock issues in serveral services.
\item Hand-on experience with Azure Event hub, Cosmos DB, Azure SQL server, Azure Redis.
as part of application re-write.
\item Developed test automation framework using Specflow for product testing.
\item Domain - Hedge Fund
\end{tightemize}
\sectionsep

\runsubsection{Publicis Sapient}
\descript{| Junior Associate Technology }
\location{Dec 2021 – June 2022 | Gurgaon, Haryana}
\begin{tightemize}
\item Worked on .NET Core Web API, Angular 10, CosmosDB and SQL Server.
\item Worked on creating, automating, executing Test Scenarios along with defect logging and triaging.
\item Worked closely with DEVOPS, QA and BA teams to ensure smooth and timely delivery.
\item Domain - Regulatory Reporting
\end{tightemize}
\sectionsep



\runsubsection{Nagarro}
\descript{| Associate Engineer}
\location{July 2021 – Dec 2021 | Gurgaon, Haryana}
\begin{tightemize}
\item Worked on an E-Commerce project using technologies like .NET Framework, Angular 6, Redis and SQL Server.
\item Resolved multiple UI related issues and optimized the product search feature for 40\% improvement.
\end{tightemize}
\sectionsep

\runsubsection{Nagarro}
\descript{| Trainee}
\location{Jan 2021 – June 2021 | Gurgaon, Haryana}
\begin{tightemize}
\item Got trained on .NET Core, C\# and other related Microsoft technologies like SQL Server, Azure Devops.
\item Also, learned JWT authentication, serialization, Messaging Queues, Event Hub and built a project around it for learning.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{T-Shirt Store}
\descript{| MERN}
Ecommerce website built using MERN(Mongo, Express.js, react.js, node.js) Stack. Authentication, admin panel and
PayPal integration are also implemented in this build.  
\sectionsep

\runsubsection{NCR Book Events}
\descript{| .NET Core \& SQL Server}
A web application build using .NET Core, Bootstrap, Javascript and SQL. It can share information about the events, send
private invites to individuals and an admin portal for management of all the event data
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certificates
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certificates} 
\begin{tabular}{ll}
AZ-900: Microsoft Azure Fundamentals	     & 04/2022\\
Coding Ninjas : Data Structures in JAVA	     & 07/2020\\
A2IT PVT. LTD : Python Programming                        & 06/2019\\
\end{tabular}
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}
